\sysfull

### 2018-04-14 paper/partialcommit.tex
small fixes cleanup

\subsection{Task Downsizing} %Partial Commit/Partial Execution

@@

If power fails consecutively twice before the system can complete one single static task, it means that the static task requires more energy than currently available in a discharge cycle, so it is necessary to have a mechanism to execute a chunk of the task, save the partial progress through the task, and continue try to run the rest of the task.  If a power failure occurs after saving partial task progress, the system makes forward progress, albeit without task atomicity. Coala may save partial task progress multiple times before completing a very long task.  To avoid the fail-stop case of non-termination, Coala's partial commit mechanism will split tasks that have not been marked as atomic by the programer.

@@

Coala starts with a big random guess and down-scales it using a binary search until it succeeds in preserving the partial execution progress. The obtained value is the initial seed for the next partial commit procedure.

@@

\subsection{Why partial commit is not Coala's default behavior}

\emph{Static deployment of partial commit stubs} This approach reduces programmer effort - they still need to apply Coala's API and distribute trigger points for partial commits - but it introduces an additional overhead by saving the stack and the register file each time it commits the pages.

>>>>

\subsection{Task Downsizing}
\label{sec:task_downsizing}

@@

If power fails consecutively twice before the system can complete one single static task, it means that the static task requires more energy than currently available in a discharge cycle, so it is necessary to have a mechanism to execute a chunk of the task, save the partial progress through the task, and continue try to run the rest of the task. If a power failure occurs after saving partial task progress, the system makes forward progress, albeit without task atomicity. \sys may save partial task progress multiple times before completing a very long task. To avoid the fail-stop case of non-termination, \sys's partial commit mechanism will split tasks that have not been marked as atomic by the programmer.

@@

\sys starts with a big random guess and down-scales it using a binary search until it succeeds in preserving the partial execution progress. The obtained value is the initial seed for the next partial commit procedure.

@@

\subsection{Why partial commit is not \sys's default behavior}

\emph{Static deployment of partial commit stubs} This approach reduces programmer effort---they still need to apply \sys's API and distribute trigger points for partial commits---but it introduces an additional overhead by saving the stack and the register file each time it commits the pages.
